---
title: >
  The `SLOcatoR` User's Guide
author:
- name: Ramon Massoni-Badosa
  affiliation: 
  - TODO
  email: TODO
- name: Federico Marini
  affiliation: 
  - Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), Mainz
  email: marinif@uni-mainz.de

date: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('SLOcatoR')`"
output: 
  BiocStyle::html_document:
    toc_float: true
vignette: >
  %\VignetteIndexEntry{The SLOcatoR User's Guide}
  %\VignetteEncoding{UTF-8}  
  %\VignettePackage{SLOcatoR}
  %\VignetteKeywords{GeneExpression, RNASeq, FunctionalAnnotation, Sequencing, Visualization, QualityControl, GUI}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
bibliography: SLOcatoR.bib
---

<style type="text/css">
.smaller {
  font-size: 10px
}
</style>

**Compiled date**: `r Sys.Date()`

**Last edited**: 2023-06-13

**License**: `r packageDescription("SLOcatoR")[["License"]]`

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  error    = FALSE,
  warning  = FALSE,
  eval     = TRUE,
  message  = FALSE,
  fig.width = 10
)
options(width = 100)
```

<hr>

# Introduction {#introduction}

This vignette describes how to use the `r BiocStyle::Biocpkg("SLOcatoR")` package for ...

Blah blah [@MassoniBadosa2022]

# Getting started {#gettingstarted}

To install this package, start R and enter:

```{r install, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")

BiocManager::install("SLOcatoR")
```

Once installed, the package can be loaded and attached to your current workspace as follows:

```{r loadlib, eval = TRUE}
library("SLOcatoR")
```

## All set!

Once you have ...

```{r}

```

you are good to go

# The `SLOcatoR` functionality {#functionality}

The main `SLOcatoR` package can...

# Use case 1: Transfer label microenvironment cells {#usecase1}

following the vignette you link in the README

# Use case 2: Harmonize CITE-seq object CD8 T {#usecase2}

following the vignette you link in the README

# Additional Information {#additionalinfo}

Bug reports can be posted on the Bioconductor support site (https://support.bioconductor.org/) or raised as issues in the `SLOcatoR` GitHub repository... 

If you use `SLOcatoR` for your analysis, please cite it as shown below:

```{r cite}
citation("SLOcatoR")
```


# FAQs {#faqs}

**Q: `TODO Can I do x with SLOcatoR`????**

A: TODO You can do it!


# Session Info {- .smaller}

```{r sessioninfo}
sessionInfo()
```

# References {-}
